---
title: "Titanic"
author: "Chinki"
date: "April 10, 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
Titanic Machine learning from Disaster.

Data Collection:
source-https://www.kaggle.com/c/titanic/data
Data has two group training and test.
Data description 
Variable	Definition	Key
survival	Survival	0 = No, 1 = Yes
pclass	Ticket class	1 = 1st, 2 = 2nd, 3 = 3rd
sex	Sex	
Age	Age in years	
sibsp	# of siblings / spouses aboard the Titanic	
parch	# of parents / children aboard the Titanic	
ticket	Ticket number	
fare	Passenger fare	
cabin	Cabin number	
embarked	Port of Embarkation	C = Cherbourg, Q = Queenstown, S = Southampton
```{r getwd, echo=FALSE}
wd <- getwd()
```

```{r Read_data}
# Reading data
Titanic_traning=read.csv(file.path(wd, "train.csv"))
Titanic_test=read.csv(file.path(wd, "test.csv"))
```

Data exploring and preparing 
```{r}
#No of male and Females in titanic training data 
table(Titanic_traning$Sex,Titanic_traning$Survived,Titanic_traning$Pclass)
```

```{r}
# No of male and females in test data set
table(Titanic_test$Sex,Titanic_test$Pclass)
```

```{r}

Titanic_traning$Sex=factor(Titanic_traning$Sex)
barplot(prop.table(table(Titanic_traning$Sex)),col = "blue")
```
```{r}
# examine the structure of dataset
str(Titanic_traning)
```
```{r}
Titanic_traning$Survived=factor(Titanic_traning$Survived,levels = c("0","1"),labels = c("survived","notsurvived"))
```

```{r}
#checking for missing values 
sapply(Titanic_traning,function(x) sum(is.na(x)))
```

```{r}
#Find out unique values from data set
sapply(Titanic_traning,function(x) length(unique(x)))
```
```{r}
# Dummy variable
contrasts(Titanic_traning$Sex)
```
```{r}
#Dummy variable 
contrasts(Titanic_traning$Embarked)
```
```{r}
#Checking for missing value
table(is.na(Titanic_traning$Embarked))
```
```{r}
#Checking for missing value of age 
table(is.na(Titanic_traning$Age))

```
```{r}
#In tarining data set 177 missing values
Titanic_traning$Age[is.na(Titanic_traning$Age)]=mean(Titanic_traning$Age,na.rm = T)
```
Now we are ready to run Algorithum 
We will delete unnessecary data columns from data set.
```{r}
Titanic_traning=Titanic_traning[c(2,3,5,6,7,8,10,12)]
```

```{r}
#Logistic Regression model
result=glm(Survived~.,family = binomial(link = "logit"),data = Titanic_traning,control = list(maxit = 1500))
summary(result)
```
```{r}
anova(result,test = "Chisq")
```

```{r}
predict=predict(result,newdata = subset(Titanic_test,select=c(2,4,5,6,7,8,9,10,11)))
```

